---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(dplyr)
```

```{r}
book_data <- read.csv("data/books.csv")
```


Questions 

1. What are the top 5 books with the highest rating book not in English

```{r}

book_data %>% 
  select(title, language_code, average_rating) %>% 
  filter(!language_code %in% c("eng", "en-US", "en-CA", "en-GB")) %>% 
  arrange(desc(average_rating)) %>% 
  head(5)

#couldnt get the contains function to work here?
  
```

2.  books that have a rating of 5?  

```{r}
books_with_five_rating <- book_data %>% 
  select(title, publisher, average_rating) %>% 
  filter(average_rating == 5.00)

books_with_five_rating

```
3. which publisher is most common with a five star rating 

```{r}
books_with_five_rating %>% 
  group_by(publisher) %>% 
  summarise(total_times = n(),
            .groups = "drop") %>% 
  arrange(desc(total_times))
```

4. In the years between 1995 and 2000 what was the average book size?

```{r}

book_data %>% 

  select(publication_date, num_pages) %>% 
  # mutate(publication_date = as.double(publication_date)) %>% 
  filter(publication_date > "1/1/1995") %>% 
  filter(publication_date < "31/12/1999") %>% 
  summarise(mean(num_pages))

#not sure how to get working 
         
```


5. total number of text and ratings reviews on a book - which book had the most ratings? 

```{r}
book_data %>% 
  select(title, ratings_count, text_reviews_count) %>% 
  mutate(total_review_raitng_count = ratings_count + text_reviews_count) %>% 
  arrange(desc(total_review_raitng_count)) %>% 
  head(1)
```

6. which publishing date has the most reviews?

```{r}
book_data %>% 
  mutate(total_review_raitng_count = ratings_count + text_reviews_count) %>% 
  select(text_reviews_count, publication_date) %>% 
  arrange(desc(text_reviews_count)) %>% 
  head(1)
```
7. which authors most common in books rated from 4-5

```{r}
books_with_five_rating_author <- book_data %>% 
  select(title, authors, average_rating) %>% 
  filter(average_rating > 4.00) %>% 
  group_by(authors) %>% 
  summarise(total_times = n(),
            .groups = "drop") %>% 
  arrange(desc(total_times))

books_with_five_rating_author %>% 
  head(1)
```


In class questions 

1. how many books in each language?

```{r}

books_per_language <- books %>% # assign to new df to reuse later
  group_by(language_code) %>% 
  summarise(num_of_books = n()) %>%  # Number of books in each language
  arrange(desc(num_of_books))

books_per_language

#could use count

book_data %>% 
  count(language_code)

```

2. Any similatries betwwen top rated books - also rempove not a book, and at least have 100 rating

```{r}

purged <- book_data %>% 
  filter(!authors == "NOT A BOOK")

purged %>% 
  filter(ratings_count >= 100) %>% 
  slice_max(average_rating, n = 5)

```
3. do more recently published book revive a higher reviews than older 

```{r}
book_data %>% 
  filter(ratings_count > 1) %>% 
  select(title, authors, publication_date, average_rating) %>% 
  mutate(as.Date(publication_date, "%m %d %Y"))
```

