---
title: "R Notebook"
output: html_notebook
---
## load librarys 

```{r}
library(tidyverse)
library(dplyr)
```
## read in data 

```{r}
book_data <- read.csv("data/books.csv")
```

## Lets look at the data 

```{r}
nrow(book_data)
ncol(book_data)
dim(book_data)
names(book_data)
head(book_data)
tail(book_data)
glimpse(book_data)
view(book_data)
summary(book_data)

```

Questions 

1. What are the top 5 books with the highest rating book not in english

```{r}

book_data %>% 
  select(title, language_code, average_rating) %>% 
  filter(!language_code %in% c("eng", "en-US", "en-CA", "en-GB")) %>% 
  arrange(desc(average_rating)) %>% 
  head(5)

#couldnt get the conatains function to work here?
  
```

2.  books that have a raiting of 5?  

```{r}
books_with_five_rating <- book_data %>% 
  select(title, publisher, average_rating) %>% 
  filter(average_rating == 5.00)

books_with_five_rating

```
3. which publish is most common with a five star rating 

```{r}
books_with_five_rating %>% 
  group_by(publisher) %>% 
  summarise(total_times = n(),
            .groups = "drop") %>% 
  arrange(desc(total_times))
```

4. In the years between 1995 and 2000 what was avarage book size 

```{r}

book_data %>% 

  select(publication_date, num_pages) %>% 
  filter(publication_date > "1/1/1995") %>% 
  filter(publication_date < "31/12/1999") %>% 
  summarise(mean(num_pages))

         
```


5. total number of text and ratings reviews recived on a book - which book recived the most ratings? 

```{r}
book_data %>% 
  select(title, ratings_count, text_reviews_count) %>% 
  mutate(total_review_raitng_count = ratings_count + text_reviews_count) %>% 
  arrange(desc(total_review_raitng_count)) %>% 
  head(1)
```

6. which publishing date has the most reviews

```{r}
book_data %>% 
  mutate(total_review_raitng_count = ratings_count + text_reviews_count) %>% 
  select(text_reviews_count, publication_date) %>% 
  arrange(desc(text_reviews_count)) %>% 
  head(1)
```
7. which auther most commin in books ratie from 4-5

```{r}
books_with_five_rating_author <- book_data %>% 
  select(title, authors, average_rating) %>% 
  filter(average_rating > 4.00) %>% 
  group_by(authors) %>% 
  summarise(total_times = n(),
            .groups = "drop") %>% 
  arrange(desc(total_times))

books_with_five_rating_author %>% 
  head(1)
```
```

