---
title: "R Notebook"
output: html_notebook

---

#learning obj

- Know how to include HTMN in a shiny app 
_ know how to include CSS in a shiny app
- be able to use themes and UI layouts in shiny 

so far we've looked at simple UIs
shiney also allows us to fully customise the app's design using 
Shiny functions, HTML, CSS or Javascript inswde the apps code 
- alsp pre-exsitn thense we can us e


#HTML
Hypertext Markup Lanagauga - standered lanf use to define webpage structure

Can elave the UI of a shiny app by adding custom HTML not orivide by shines

E.G <i> text </i> for italics

#using tags for HTML 

Rneeds to be able to understand what is R code and what is HTML etc

can use functions inside `tags` from the shiny package 

e.g italices 
```{r}
tags$i("some text")
```

```{r}
tags$b("hello")
```


e.g attributes (can be given to the tage with named argument )

```{r}

tags$a("Codeclan's Website", href = "https://codeclan.com")

```


# Themes 

You canquculiy change the look of your app by using any one of the thmese aviavile in the `bslib` package rather than worry anout 
HTML and CSS

cheeck out bootswatch.com to see them all 

Inside the `fluidpage` fucntion give the theme argumnet a vaule 

`theme = bs_theme(bootswatch = "name of theme")`

e.g

```{r eval = FALSE}

library(bslib)

ui <- fluidPage(
  theme = bs_theme(bootswatch = "flatly"),
)

```


By far the eaisest way to contol the way your UI looks 

Can write your own custom themes, but that involves something called CSS


- in the notes if intersted 

# Other layouts 

so far we been using sidebar layout  - lots of other avaialbe 


Today we will the grid layout and adding tabs 

use `fluid row` with `colunm` and `width` to specifiy where on the gruid our wdigets go 

#tabs 

can be added into any layout 

you suse the function `tabsetPanel` with diffenret `tabpanel` 
elemnets inside

first argument to tabpanel is the name at the top of the tab then UI element 
```{r}


tabsetPanel(
  tabPanel("first tab",
           "first tab contenet"),
  tabPanel("second tab",
           "second tab conctect here")
  
)


```


lets edit our lympics app to have tabs instead of rows 

- a tab that only has our plot
- tab only radio buttons 
- a tab team in put 




