---
title: "R Notebook"
output: html_notebook
---


Question 1.

Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.


```{r}
library(tidyverse)
library(scales)
library(CodeClanData)



backpack <- backpack

backpack %>% 
  names()
backpack %>% 
  glimpse()
backpack %>% 
  dim()
```

The table is 100 x 9 with thr following coloumn names:
backpack_weight, body_weight ratio          
back_problems, major, year      
sex, status, units



Question 2.

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

```{r}

backpack %>% 
  ggplot() +
  aes(x = backpack_weight) +
  geom_bar() + 
  scale_y_continuous(breaks = c(2,4,6,8,10,12,14)) + 
  labs(
    title = "Weight of backpacks carried"
  )

```

Summary:

This show us that most people are carrying backpakcs with the weight of 10kg 


Question 3.

Are there differences in backpack weight between sex?


```{r}

backpack %>% 
  ggplot() +
  aes(x = backpack_weight, fill = sex) +
  geom_histogram(position = "dodge", binwidth = 1) + 
  scale_y_continuous(breaks = c(2,4,6,8,10,12,14)) + 
  labs(
    title = "Weight of backpacks carried by sex"
  ) + facet_wrap(~ sex)

count_data %>% 
  ggplot() +
  aes(x = backpack_weight, y = counts, colour = sex) +
  geom_line() + 
  scale_y_continuous(breaks = c(2,4,6,8,10,12,14)) + 
  labs(
    title = "Weight of backpacks carried by sex"
  ) + facet_wrap(~sex)

count_data <- backpack %>% 
  group_by(backpack_weight, sex) %>% 
  summarise(counts = n())

```
Summary:
Females most common weight was 10kg while male was 11kg 


Question 4.

What is the relationship between body weight and backpack weight?

```{r}

backpack %>% 
  ggplot()+
  aes(x = body_weight, y = backpack_weight) +
  geom_point()



backpack %>% 
  ggplot()+
  aes(x = body_weight, y = backpack_weight) +
  geom_col()

```

Summary: not really a relationship 


Question 5.

Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}

backpack %>% 
  ggplot()+
  aes(x = body_weight, y = backpack_weight, fill = sex) +
  geom_col() + 
  facet_wrap(~sex)
```




Question 6.

What proportion of students report back pain?

```{r}
proportions2 <- backpack %>% 
  summarise(pp = mean(back_problems)) %>% 
  pull(pp)

backpack <- backpack %>%
  mutate(backpain_labelled = recode(back_problems, 
                       "0" = "No", 
                       "1" = "Yes"))

ggplot(backpack) + 
  aes(x = backpain_labelled, fill = backpain_labelled) + 
  geom_bar() +
ylim(0,100) + 
  labs(x = "backpain reported", y = "student count") +
    scale_fill_manual(values=c('#f0ca41', '#5022bd'))+
theme(legend.position = "none")


```



Question 7.


```{r}
ggplot(backpack) + 
  aes(x = backpain_labelled, fill = backpain_labelled) + 
  geom_bar() +
  labs(x = "backpain reported", y = "student count") + 
  facet_wrap(~sex) +
      scale_fill_manual(values=c('#f0ca41', '#5022bd'))+
theme(legend.position = "none")
```


Is this proportion different between men and women?

Question 8.

Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.



```{r}
pain_labels <- c("backpain: no", "backpain: yes")
names(pain_labels) <- c("No", "Yes")

sex_labels <- c("sex: female", "sex: male")
names(sex_labels) <- c("Female", "Male")


ggplot(backpack) + 
  aes(x = body_weight, y = backpack_weight, color = backpain_labelled) + 
  geom_col() + 
  facet_grid(sex ~ backpain_labelled, 
             labeller = labeller(backpain_labelled = pain_labels, sex = sex_labels)) + 
  labs(x = "\n body weight", y = "backpack weight \n") +
      scale_color_manual(values=c('#f0ca41', '#5022bd'))+
theme(legend.position = "none")
```



Try both backpack_weight and body_weight as well as the ratio.

Hint: faceting would be useful here.

```{r}

backpack %>% 
  ggplot(aes(x = backpain_labelled, fill = sex)) +
  geom_bar(position = "fill")


```

```{r}

backpack1 <- backpack %>% 
  mutate(back_problems = recode(back_problems,
                               "1" = "Back problem",
                                "0" = "No back problem"))

backpack1 %>% 
ggplot(aes(x = back_problems, y = after_stat(prop), group = 1)) +
  geom_bar() +    
  xlab("Back issues among students") +
  ylab("Percentage") +
  ggtitle("Percentage students with back issues") +
  scale_y_continuous(labels = scales::percent_format())
```

```{r}
backpack %>% 
  ggplot(aes(x = "", fill = back_problems)) +
  geom_bar(position = "fill") +
  theme_minimal() +
  labs(y = "proportion",
       x = "proportion of students with back pain") +
  scale_y_continuous(labels = scales::percent)
```

