---
title: "R Notebook"
output: html_notebook
---


Question 1.

Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.


```{r}
library(tidyverse)
library(scales)
library(CodeClanData)



backpack <- backpack

backpack %>% 
  names()
backpack %>% 
  glimpse()
backpack %>% 
  dim()
```

The table is 100 x 9 with thr following coloumn names:
backpack_weight, body_weight ratio          
back_problems, major, year      
sex, status, units



Question 2.

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

```{r}

backpack %>% 
  ggplot() +
  aes(x = backpack_weight) +
  geom_bar() + 
  scale_y_continuous(breaks = c(2,4,6,8,10,12,14)) + 
  labs(
    title = "Weight of backpacks carried"
  )

```

Summary:

This show us that most people are carrying backpakcs with the weight of 10kg 


Question 3.

Are there differences in backpack weight between sex?


```{r}

backpack %>% 
  ggplot() +
  aes(x = backpack_weight, fill = sex) +
  geom_histogram(position = "dodge", binwidth = 1) + 
  scale_y_continuous(breaks = c(2,4,6,8,10,12,14)) + 
  labs(
    title = "Weight of backpacks carried by sex"
  ) + facet_wrap(~ sex)

count_data %>% 
  ggplot() +
  aes(x = backpack_weight, y = counts, colour = sex) +
  geom_line() + 
  scale_y_continuous(breaks = c(2,4,6,8,10,12,14)) + 
  labs(
    title = "Weight of backpacks carried by sex"
  ) + facet_wrap(~sex)

count_data <- backpack %>% 
  group_by(backpack_weight, sex) %>% 
  summarise(counts = n())

```
Summary:
Females most common weight was 10kg while male was 11kg 


Question 4.

What is the relationship between body weight and backpack weight?

```{r}

backpack %>% 
  ggplot()+
  aes(x = body_weight, y = backpack_weight) +
  geom_line() + 
  geom_point()



backpack %>% 
  ggplot()+
  aes(x = body_weight, y = backpack_weight) +
  geom_col()

```

Summary: not really a relationship 


Question 5.

Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}

backpack %>% 
  ggplot()+
  aes(x = body_weight, y = backpack_weight, fill = sex) +
  geom_col() + 
  facet_wrap(~sex)
```




Question 6.

What proportion of students report back pain?

```{r}
proportions2 <- backpack %>% 
  summarise(pp = mean(back_problems)) %>% 
  pull(pp)


```



Question 7.

Is this proportion different between men and women?

Question 8.

Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

Try both backpack_weight and body_weight as well as the ratio.

Hint: faceting would be useful here.

