---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
source("prob.R")
library(gtools)
```


```{r}
titanic <- read_csv("dataa/titanic.csv")
```

```{r}
titanic %>% 
  distinct(class)
```

```{r}

titanic_class <- titanic %>% 
  mutate(passanger = str_detect(class, pattern = "1st|2nd|3rd")) %>% 
  relocate(passanger, .after = class)

titanic_class_filtered <- titanic_class  %>% 
  select(passanger, survived)
  

```

if true they are passangers 

```{r}
titanic_tab <- titanic_class_filtered %>%
  tabyl(passanger, survived) %>% 
  adorn_totals(where = c("row", "col")) 
  


```

```{r}

titanic_tab <- titanic_class_filtered %>%
  tabyl(survived, passanger) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all")
  


```
TRUE = PASSANGER 
FALSE = CREW 
prob (s | c)

prob(s = 0.32215677
p(s and C) = 0.09560489
p(c) = 0.40326235

p(A AND B) == p(A) * p(B)

0.32215677 * 0.40326235 
doeenst = ( so its a dependednt event )

p(A | B) = p(A and B)/ p(B)

0.09560489 / 0.40326235

Answer: 0.2370786

Survied / passenger 

prob(s = 0.32215677
p(p) = 0.5967377
p ( s and P) = 0.2265519

0.32215677 * 0.5967377

=0.1922431 so its dependednt 

p(A | B) = p(A and B)/ p(B)

0.2265519 / 0.5967377

Answer:  0.3796507

Question 1.
If I roll a six-sided dice once, what is the probability of getting a number less than 5?

6 outcomes 
4 can be true  

4/6
= 2/3

Question 2.
How many outcomes are there in the sample space of an experiment in which we toss three dice?
6^3
216 outcomes 

Question 3.
In an experiment where we roll four dice:

how many outcomes are in the event where the total of the four dice equals 5
, 6
 or 7
)?
what is the probability of this event?  `p = 9/1296, = 1/144 = 0.0069444`
what assumptions do we apply in answering part ii?
Hint
For part i, rowSums(.) may help you setup up the necessary random variable total (or you can use pivot_longer())

total outcomes = 6^4 = 1296

```{r}
four_dice <- rolldie(4,6)

four_dice %>% 
  mutate(total = X1 + X2 + X3 + X4) %>% 
  filter(total == c(5,6,7))


```

Question 4.
Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

Hint


5! = 120 = possiablitys with 1 chance it being in order


120 / 1

= 1/120 = 0.0083



