---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(cluster)
library(factoextra)
library(dendextend)
library(broom)
```


```{r}
mall <- read_csv("../mall_customers.csv")
```


Task 1

Do some exploratory analysis on the data. Comment on findings.


```{r}
mall %>% 
  skimr::skim()
```
Data is well distributed
Each row is a Customer which age, gender with there income and income score 


Task 2

We are interested in creating a marketing campaign to target customers based on their spending score and annual income. Select an appropriate value for k and perform k-means clustering to find if there are meaningful clusters in the data to target the customers.


```{r}
mall_scale <-
mall %>% 
  select(`Annual Income (k$)`, `Spending Score (1-100)`) %>% 
  mutate(across(where(is.numeric), scale))
```



```{r}

max_k <- 25

mall_clusters <- tibble(k = 1:max_k) %>% 
  mutate(kclust = map(k, ~ kmeans(mall_scale, .x, nstart = 50)),
         tidied = map(kclust, tidy),
         glanced = map(kclust, glance),
         augmented = map(kclust, augment, mall_scale))

```

```{r}
mall_clusters_out <- mall_clusters %>% 
  unnest(glanced)
```

elbow:

```{r}

ggplot(mall_clusters_out, aes(x = k, y = tot.withinss)) +
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks = seq(1, 20, by = 1))

```
silhouette 

```{r}

fviz_nbclust(mall_scale,
             kmeans,
             method = "silhouette",
             nstart = 50)

```
```{r}

fviz_nbclust(mall_scale,
             kmeans,
             method = "gap_stat",
             nstart = 50,
             k.max = 10)

```
I think 5 clusters 

```{r}
clustered_mall <- kmeans(mall_scale,
                             centers = 5,
                             nstart = 100)
```


```{r}

mall_with_clusters <-
augment(clustered_mall, col.names = colnames(mall_scale), data = mall_scale)

```


Task 3

Visualise the clustering for your chosen value of k.


```{r}
mall_with_clusters %>% 
  ggplot(aes(x = `Annual Income (k$)`, y = `Spending Score (1-100)`)) +
  geom_point(aes(col = .cluster)) 

```



Task 4

Do you think the clustering seems a good fit for this data?

I think it looks pretty good! 
the groups look how they would if my human eye was to do it! 



Task 5

Comment on the attributes of one or two of the clusters (maybe even give them an appropriate label if you like - similar to section 4.1 of the ‘Segmentation & clustering intro’ lesson where we saw labels such as “Super Fans” and “Tag-Alongs”).

```{r}
fun <-
mall_with_clusters %>% 
  mutate(.cluster = case_when(str_detect(
                                         .cluster, "1") ~ "Big money no spend",
                              str_detect(.cluster, "2") ~ "Big Money Big Spend",
                              str_detect(.cluster, "3") ~ "No Money No spend",
                              str_detect(.cluster, "4") ~ "No Money still spend!!",
                              str_detect(.cluster, "5") ~ "Average at both"))


```

```{r}
fun %>% 
  ggplot(aes(x = `Annual Income (k$)`, y = `Spending Score (1-100)`)) +
  geom_point(aes(col = .cluster)) 

```

