---
title: "R Notebook"
output: html_notebook
---

1 MVP
Now we’ll go back to CI creation in the normal fashion. We’ll take the ames data from the CIs lab earlier today and regard it now as a sample, we won’t be drawing any smaller samples from within it. This is the usual situation in an analysis: you use all the data available to you!

```{r}
library(tidyverse)
library(infer)
library(janitor)
```


Task 1.
Load the data again, clean_names(), and re-familiarise yourself with it

```{r}
ames <- read_csv("data/ames.csv") %>% clean_names()
```


Task 2.
Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?


```{r}

ames %>% 
  ggplot(aes(x = lot_area)) +
  geom_boxplot()
  

```

very skewed, lots of outlieres

Task 3.
Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.

```{r}

infer_ames <- ames %>% 
  specify(response = lot_area) %>% 
  generate(reps = 5000, type = "bootstrap") %>% 
  calculate(stat = "mean")
  

```


Task 4.
Use your bootstrap distribution to calculate a 95%
 CI for mean(lot_area), and visualise it on the distribution

```{r}

infer_ci <- infer_ames %>% 
  get_ci(level = 0.95, type = "percentile")

infer_ames %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = infer_ci)

```


Task 5.
You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99%
 CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95%
 CI? Does that make sense?

```{r}
infer_ci_99 <- infer_ames %>% 
  get_ci(level = 0.99, type = "percentile")

infer_ames %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = infer_ci_99)


```
the 99% is broder = as the CI for 95% is [99,105] when 99% [98,106]
99% is cap more data 

Task 6.
Calculate the point estimate of the mean(lot_area)


```{r}

infer_ames %>% 
  summarise(mean = mean(stat))

```
mean = 10150.58

2 Extension


Task 1.
Calculate a point estimate and 95%
 CI for the proportion of houses in the data built before 1920. Does the number of reps you use matter? [Investigate reps from 200
 up to 50000
, memory of your laptop permitting].

```{r}


ames <- ames %>% 
  mutate(before_1920 = case_when(
    str_detect(year_built, pattern = "\\b(0|1[0-8]{0,2}|19[0-1][0-9])\\b") ~ "Yes",
    .default = "No")) %>% 
  relocate(before_1920, .before = year_built)

```




```{r}
infer_ames_1920 <-ames%>% 
  specify(response = before_1920, success ="Yes") %>% 
  generate(reps = 5000, type = "bootstrap") %>% 
  calculate(stat = "prop")
  

```

```{r}

before_ci_95 <- infer_ames_1920 %>% 
  get_ci(level = 0.95, type = "percentile")


```
```{r}
infer_ames_1920 %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = before_ci_95)

```

```{r}



```

