---
title: "R Notebook"
output: html_notebook
---

#obj

-- know how to crrat a basic shiny app
-- understand how to use imputs and outputs to create interactivity

# whats a shiny app 

Its a way of developing interactive web applications thorught writting r code 
- interactive exploriont of data
- can be basic, can be very complicated


# Basic shinny app

```{r eval = FALSE}

library(shiny)

ui <- fluidPage() #defin e the user interface (determines the layout and apperance of the app, you can use other but this will do)

server <- function(input, output) {
  #define the server, this defines the logic of our app
  
}

shinyApp(ui = ui, server = server) #run fucntion with ui and serevr as inputs

```


You can add more ui emlements inside both the sidepabpanel and the main panale, sepearted by a comma

use `br()` to add line breaks

lots of layouts available - can see this in the shiny doc 

# widgets 

the interactibe parts of teh app and have the basic stucters

```{r eval = FALSE}
 
widgetInput(inpitID = "id", # serverr frienly widget lable
            label = "widget label", # human friendly widget label,
            choices = c("choice A", "choice B")
            
            )

```

Lets out some radio buttion in our sidebar ]


```{r eva = FALSE}

radioButtons(inputId = "season_input",
             label = "Summer or Winter Olympics?",
             choices = c("Summer", "Winter"))

```

Current radio buttons not connect to anything in the sever logic

- we,ve only changed the ui 

Add a selectInput widget to the UI that allows you to choose between the teams “United States”, “Soviet Union”, “Germany”, “Italy”, and “Great Britain”.


```{r}

radioButtons(inputId = "country_input",
             label = "Country",
             choices = c("United States", "Soviet Union", "Germany", "Italy", "Great Britain"))


```

#The server

While the UI defines how our app looks the server is everything that haapnes behing the sceen 

Deals with inputs from the user/UI and creats outpots for the app 

## Creating outputs 

The key word here is 'render
e.g to make a plot output we use 'render Plot' to creat  a text output we use 'rendertext, a table needs 'renderTable

Lets ,ale a simple plot showing medlas won by briten in the summer olymics

```{r}

library(tidyverse)

olympics_overall_media <- read_csv("2_basic_shiny_apps/data/olympics_overall_medals.csv")

```

```{r}

olympics_overall_media %>% 
  filter(team == "Great Britain") %>% 
  filter(season == "Summer") %>% 
  ggplot() +
  aes(x = medal, y = count, fill = medal)+
  geom_col(show.legend = FALSE)
  

```

Okay se we have a plot that works, now we need to"

1. wrap the code in render plot 
2. assing vaule to an output slot 
3. put this all inside the server function 
4. chnage the UI accordinly 

currenlty the inputs and outputs are not connected so the plots doesnt change when we select countries/seasons 

#using inputs 

These come from the widgets - inputs will have dif vaules depending action of the user

e.g. summer or winter - reffere to as `input$season_input`

```{r eval = FALSE}
# in ui:
selectInput("team_input",
          "Which Team?",
          choices = c("United States",
                      "Soviet Union",
                      "Germany",
                      "Italy",
                      "Great Britain")
          
# in server:
output$medal_plot <- renderPlot({

    olympics_overall_medals %>%
      filter(team == input$team_input) %>%
      filter(season == input$season_input) %>%
      ggplot() +
      aes(x = medal, y = count, fill = medal) +
      geom_col()
  })
```

#code outside the ui and server

we placed liabry call before ui and server
- run as soon as the app is lanched
- makes it easy to write code that can be used by either ui or server

could make an object here of all team names 

```{r}
all_teams <- olympics_overall_media %>% 
  distinct(team) %>% 
  pull()
```

There we go an app!!

# tips 

shiny is tricky, hard to keep track of wehat everything does and keeps the brackets organies 


- indernrs everything correclty 
- ranbow brackets 
- look at red x in margin 
- click next to a brackt to higlet everything in it 
- the error: `Error in tag("div", list(...)): argument is missing no defualt` or silmals means extar comma somewhere 