---
title: "R Notebook"
output: html_notebook
---

Question 1.
Load the data, clean_names() and explore it.

```{r}
library(tidyverse)

clean_names <- read.csv("20190928-items.csv")

clean_names %>% 
  skimr::skim()

```

```{r}
clean_names %>% 
  ggplot(aes(x = rating)) +
  geom_histogram()
```
`data is negative scweked `
`unimodel`




Question 2.
Find the brand with the highest numbers of phones in the dataset.

```{r}
clean_names %>% 
  group_by(brand) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count)) %>% 
  head(1)
  
```



Question 3.
For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. Do you think the normal distribution provides a good model of these ratings?
Hint

```{r}


  
samsung %>% 
  skimr::skim(rating)

samsung_stats <- samsung %>% 
  summarise(
    num = n(),
    mean = mean(rating),
    sd = sd(rating)
  )

samsung <- clean_names %>% 
  filter(brand == "Samsung") %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = after_stat(density)),
                 col = "white",
                 bins = 20) +
  stat_function(
    fun = dnorm,
    args = list(mean = samsung_stats$mean,
                sd = samsung_stats$sd),
    col = "green"
  )
  


```
mean = 3.5733
sd = 0.6

`not the best lots of stuff left out!`
`stops before end of rating`

Question 4.
We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. You calculated the mean() and sd() of your distribution in an earlier question. Use these values to calculate the proportions of ratings within one-, two- and three standard deviations of the mean. Compare these proportions with those you expect for a normal distribution.

This is what we expect =
```{r}
pnorm(1) - pnorm(-1)
pnorm(2) - pnorm(-2)
pnorm(3) - pnorm(-3)

```

```{r}

samsung %>% 
 filter(rating >= samsung_stats$mean - samsung_stats$sd) %>% 
 filter(rating <= samsung_stats$mean + samsung_stats$sd) %>% 
 summarise(prop_within_1sd = n() / nrow(samsung))

```
so in 1 SD - we have more data than the three sigma rule of `0.6826895` = 0.7934509	


whats in 2 and 3 ?

```{r}

samsung %>% 
 filter(rating >= samsung_stats$mean - samsung_stats$sd) %>% 
 filter(rating <= samsung_stats$mean + samsung_stats$sd) %>% 
 summarise(prop_within_1sd = n() / nrow(samsung))


```




just me looking at stuff

```{r}
standard_scaled <- samsung %>% select(-url, -title, -image,) %>% 
  mutate(z_rating = (rating - mean(rating))/sd(rating),
         z_rating_scale = scale(rating))

standard_scaled %>% 
  filter(!between(z_rating, left = -3, right = 3))
#these are outliers!
```

```{r}

standard_scaled %>% 
  ggplot(aes(x = z_rating)) +
  geom_histogram()

```

