---
title: "Wine"
output: html_notebook
---

```{r}
library(tidyverse)
library(leaps)
library(GGally)

```

read data in
```{r}
red <- read_csv("data/wine_quality_red.csv")
white <- read_csv("data/wine_quality_white.csv")

```

add colum for red and white to the bind data 

```{r}
test <- bind_rows(.id = "wine_id", white, red)

```

each row is a different wine 



```{r}
test %>% 
  group_by(wine_id) %>% 
  summarise(count = n())
```

1 is white 
2 is red 

```{r}
test_wine <-
test %>% 
  mutate(wine_id = if_else(wine_id == 1, TRUE, FALSE)) %>% 
  rename("white_wine" = "wine_id") %>% 
  select(-region)

```

```{r}
test_wine %>% 
  summarise(across(.fns = ~ sum(is.na(.x))))
```


```{r}
skimr::skim(test_wine) %>% view()
```


```{r}
regwine_best <- regsubsets(quality ~ .,
                           test_wine,
                           nvmax = 15,
                           method = "exhaustive")

summary(regwine_best)
```

```{r}
plot(regwine_best, scale = "adjr2")
plot(regwine_best, scale = "bic")
plot(summary(regwine_best)$bic, scale = "b")
```

from this would use 5

```{r}

modelnew <- lm(quality ~ white_wine + volatile_acidity + residual_sugar + sulphates + alcohol, test_wine)

```

```{r}
plot(modelnew)
```






**********************************************

non auto 


```{r}

ggpairs(test_wine)


```

```{r}

ggsave("ggpairs.png",
       width = 20,
       height = 20)

```



```{r}
regwine_best <- regsubsets(quality ~ .,
                           test_wine,
                           nvmax = 15,
                           method = "forward")

summary(regwine_best)
```



```{r}
regwine_best <- regsubsets(quality ~ .,
                           test_wine,
                           nvmax = 15,
                           method = "backward")

summary(regwine_best)
```


```{r}
plot(regwine_best, scale = "adjr2")
plot(regwine_best, scale = "bic")
plot(summary(regwine_best)$bic, scale = "b")
```

```{r}
plot(regwine_best, scale = "adjr2")
plot(regwine_best, scale = "bic")
plot(summary(regwine_best)$bic, scale = "b")
```

**********************************

In class 

```{r}
red <- read_csv("data/wine_quality_red.csv")
white_wine <- read_csv("data/wine_quality_white.csv")

```

#what fopdness of fit measure?   adj-r2, AIC, BIC
#test train split, yes: 90/10
# k fold ? yes - to prevent over-fitting
# model? or model? red/white - separalty 

#white wine 


test train split 
```{r}
n_data_white <- nrow(white_wine)

test_index_white <-  sample(1:n_data_white, size = n_data_white*0.1)

test_white <- slice(white_wine, test_index_white)
train_white <- slice(white_wine, -test_index_white)



```
# exploer the data 
# what does 1 row look like 

1 wine with techinical measuremnts and summariesd avg ratitng 


```{r}
skimr::skim(test_white)
```

```{r message=FALSE}

train_white %>% 
  select(quality, -wine_id, 2:7) %>% 
  ggpairs()

```
```{r message=FALSE}

train_white %>% 
  select(quality, -wine_id, 8:14) %>% 
  ggpairs()

```
What transofations 

```{r}

train_white_fe <- train_white %>% 
  mutate(across(where(is.numeric), .fns = ~ log(1 + .x),
                .names = "log_{.col}")) %>% 
  mutate(chlorides_diff_to_mean = chlorides - mean(chlorides), .after = chlorides) %>% 
  mutate(chlorides_abs_to_mean = abs(chlorides_diff_to_mean), .after = chlorides_diff_to_mean) #makes negative positve 

```


```{r}
alias(quality ~ ., train_white)
```



```{r}
ggplot(train_white_fe) +
  aes(x = chlorides_abs_to_mean, y = quality ) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r}

train_white_fe %>% 
  select(quality, starts_with("log")) %>% 
  select(1:8) %>% 
  select(starts_with("log"), quality) %>% 
  ggpairs()

```

```{r}

mod1 <- lm(quality ~ alcohol, data = train_white_fe)


```


```{r}

summary(mod1
)

```

```{r}

library(modelr)

train_white_fe %>% 
  add_predictions(mod1) %>% 
  add_residuals(mod1) %>% 
  select(1:6, resid) %>% 
  ggpairs()

```


```{r}

mod2 <- lm(quality ~ alcohol + volatile_acidity, data = train_white_fe)

summary(mod2)

```

```{r}
summary(modelnew)
```

